---
title: "Plot Graph Types"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plot Graph Types}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 6,
  comment = "#>"
)
```

```{r setup}
library(nanoAFMr)
```

## Loading AFM image

```{r}
afmd <- AFM.artificialImage(
  width = 80, height = 80, type = "calibration",
  addNoise = FALSE, verbose = FALSE
)
```

The AFM image can be displayed using graphTypes:

## graphType 1

This is the basic and default graph for an AFM image:

```{r}
q <- plot(afmd, graphType = 1, trimPeaks = 0.01)
q
```

## graphType 2

This graph has a square shape and adds a bar of length 20%; it places the scale inside the graph.

```{r}
plot(afmd, graphType = 2, trimPeaks = 0.01, color = "white")
```

The image can be saved with `ggsave` as it is graphed with ggplot.

```{r}
# g1 = plot(afmd, graphType=2, size=10, trimPeaks=0.01)
# ggsave("afm-graphtype2.png", plot = g1, dpi = 150)
```

## graphType 3

This graph type is bare and has neither length scales nor legend.

```{r}
plot(afmd, graphType = 3, trimPeaks = 0.01)
summary(afmd)
```
## graphType 4

This graph type is plain with a scale. You can also change the color and the size of the font that displays the scale.

```{r}
plot(afmd, graphType = 4, color = "white", size = 4, trimPeaks = 0.05, fillOption = "A")
```



## Red Blue Color Scheme

This graph type is bare and has neither length scales nor legend.

```{r}
plot(afmd, graphType = 1, trimPeaks = 0.01, redBlue = TRUE)
```



## Graphing 2 plots side by side

Use the package `cowplot` to create a graph with two plots. Use `save_plot` to save the graph.

```{r}
# library(cowplot)
# library(latex2exp)
# fname2 = AFM.getSampleImages(type='ibw')[1]
# afmd = AFM.import(fname2)

# g1 = plot(afmd, trimPeaks=0.01, graphType = 1) + 
#   labs(fill='h (nm)') + theme(legend.key.size = unit(1, 'char'))
# g2 = plot(afmd, no=2, trimPeaks=0.01, graphType = 1, mpt=29.6) +
#   labs(fill="A (nm)") + theme(legend.key.size = unit(1, 'char'))
# g3 = plot(afmd, no=3, trimPeaks=0.01, graphType = 1, mpt=65.5) +
#   labs(fill=TeX("$\\phi$ (deg)")) + theme(legend.key.size = unit(1, 'char'))
# g4 = plot(afmd, no=4, trimPeaks=0.01, graphType = 1) + 
#   labs(fill="z (nm)") + theme(legend.key.size = unit(1, 'char'))
# gAll = plot_grid(g1, g2, g3, g4,
#           labels=c('a','b','c','d')) 
# ggdraw(add_sub(gAll, 
#                "Showing surface morphology of a phthalocyanine thin film\n with (a) height h, (b) amplitude A, (c) phase ϕ, and \n (d) z-sensor z response. Sample / image from Gredig\n Lab, CSU Long Beach.",
#                x=0.1, hjust=0))
```


## Changing the Color Palette

You can use the `fillOption` option to change the color palette, see also `? scale_fill_viridis`. There are 8 options:


```{r}
plot(afmd, graphType = 1, fillOption = "A")
plot(afmd, graphType = 1, fillOption = "C")
plot(afmd, graphType = 1, fillOption = "E")
plot(afmd, graphType = 1, fillOption = "H")
```

```{r}
# The underlying viridis options are letters A through H.
# See ?ggplot2::scale_fill_viridis_c for current palette mapping.
```


## Adjusting the scale

```{r}
plot(afmd)
plot(afmd, setRange = c(10, 90))
```
