---
title: "Advanced AFM Image Graphing"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Advanced AFM Image Graphing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 6,
  comment = "#>"
)
```

```{r setup}
library(nanoAFMr)
library(ggplot2)
library(scales)
filename = AFM.getSampleImages(type='tiff')
afmd = AFM.import(filename)
plot(afmd)
```
 
In order to get more contrast, we can trim 1 percent of the data points as the image may not be in the middle, see the histogram.

```{r}
AFM.histogram(afmd)
```

Using the `trimPeaks` option in `plot()`, we can remove half from the top and bottom of the histogram and bunch those data points up, so that the contrast enhances.


```{r}
plot(afmd, trimPeaks = 0.01)
```

## Raster Graph

Graphing a subset of the data points using the `AFM.raster()` function to obtain the 3D data point set.

```{r}
dr = AFM.raster(afmd)
head(dr)
# data points higher than 90% of peak
lowerBound = -0.3
upperBound = 0.8
dr1 =dr[which(dr$z>lowerBound & dr$z<upperBound),]
plot(afmd, trimPeaks = 0.01) + 
  geom_raster(data=dr1,fill='white')
```
