---
title: "Setpoint"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Setpoint}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Finding the Setpoint

You can find the setpoint and other information about an AFM image by retrieving the `AFMinfo`. Here is an example:

```{r}
library(nanoAFMr)

# loading the test file 
filename = AFM.getSampleImages('ibw')
# retrieving an AFMinfo object
h = AFMinfo(filename)
```


Basic information about an image can also be viewed, once you have an `AFMinfo` object:

```{r}
# generate a summary of the AFMinfo object
summary(h)
```


Finding additional special information, using the function `AFMinfo.item`; note that the search string is case-sensitive.

```{r}
sp =  AFMinfo.item(h, 'Setpoint')
print(paste("Setpoint:",sp,"V"))
```

The names of the items can be found with the same function; here is a list of the first few item names that can be used:

```{r}
allNames = AFMinfo.item(h)
print(allNames[1:50])
```
