---
title: "ForceCurves"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ForceCurves}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(nanoAFMr)
library(ggplot2)
```

## Force versus Distance Curves

This example illustrates how to extract force versus distance spectroscopy data from Park AFM images:

```{r}
f = AFM.getSampleImages('force')
a = AFM.import(f)
a = AFM.flatten(a)
plot(a) + labs(fill="z (nm)")
```

Spectroscopy data files are recognized as such:

```{r}
AFM.dataType(a)
```


The file can be graphed like a regular AFM file, but additionally, it contains the spectroscopy data. Several channels are recorded:

```{r}
AFM.specHeader(a)
```


The data from these channels is extracted as follows:

```{r}
df = AFM.specData(a)
ggplot(df, aes(`Z Scan`, Force, col=factor(Point))) + 
  geom_point() + 
  theme_bw() +
  theme(legend.position = c(0.95,0.99),
        legend.justification = c(1,1))
```
