---
title: "Height-Height-Correlation-Function"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Height-Height-Correlation-Function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 6,
  comment = "#>"
)
```

```{r setup}
library(nanoAFMr)
library(ggplot2)
```

The Height-Height Correlation Function is discussed in the publication: [Height-Height Correlation Function to Determine Grain Size in Iron Phthalocyanine Thin Films](http://iopscience.iop.org/article/10.1088/1742-6596/417/1/012069) *Thomas Gredig, Evan A. Silverstein, Matthew P Byrne*, Journal: **J of Phys: Conf. Ser. Vol 417, p. 012069 (2013).**

It defines a correlation function $g(r)$ as follows:

$$
g(r) = <| (h(\vec{x}) - h(\vec{x}-\vec{r}) |^2 >
$$

where $h(\vec{x})$ is the height at a particular location. The height difference is computed for all possible height pairs that are separated by a distance $|\vec{r}|$. Immediately, if follows that $g(0)=0$.

For a set of images, the correlation function can be interpreted as follows:

$$
g'(r) = 2\sigma^2 \left[ 1- e^{- \left(\frac{r}{\xi}\right)^{2\alpha}} \right]
$$

which has 3 fitting parameters, the long-range roughness $\sigma$, the short-range roughness $\alpha$ (Hurst parameter), and the correlation length $\xi$.

## Example: HHCF

The computation is implemented in this package as follows, the image is flattened, then HHCF is computed and the curve is fit. Choosing a large number of iterations is crucial. The computation is executed with the `AFM.hhcf()` function.


```{r}
filename = AFM.getSampleImages(type='tiff')
a = AFM.import(filename)
a = AFM.flatten(a)
AFM.hhcf(a, numIterations= 2e5)
```

You can see the fit parameters, and make a custom plot from the data, if you export all results from the function

```{r, message=FALSE, warning=FALSE}
library(pander)
h = AFM.hhcf(a, numIterations= 2e5, allResults = TRUE)

## show the fit parameters
pander(h$fitParams)
## show the HHCF data
head(h$data)
## display the entire graph
h$graph
```
