---
title: "Line Profiles"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Line Profiles}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.height = 6
)
```

```{r setup}
library(nanoAFMr)
```

# Line Profiles

It can be useful to look at a line profile, for example in the height data. You can use `AFM.lineProfile()` to get an arbitrary line, or `AFM.getLine()`, if you want to select a horizontal line. In the example below, we provide the coordinates in units of [nm], however, you can also provide the coordinates in pixels, if you set `unitPixels` to `TRUE`. Alternatively, if you are not providing any coordinates, you can click on two points to select a profile line.

```{r}
library(ggplot2)
afmd <- AFM.artificialImage(
  width = 120, height = 120, type = "gradient",
  addNoise = TRUE, verbose = FALSE
)
# afmd2 = AFM.lineProfile(afmd)  # click on two points on the image
afmd2 <- AFM.lineProfile(afmd, 100, 300, 900, 300, verbose = TRUE)
afmd2 <- AFM.lineProfile(afmd2, 100, 700, 900, 700)

plot(afmd2, addLines = TRUE, trimPeaks = 0.01)
```

This shows where the profile line is measured; the units are in `nm`, according to the AFM image.

```{r}
AFM.linePlot(afmd2)
dLine <- AFM.linePlot(afmd2, dataOnly = TRUE)
head(dLine)
```

The line plot has a lowest point at `r signif(min(dLine$z),3)` nm, and a maximum at `r signif(max(dLine$z),3)` nm.
